---
title: "Deaths due to cardiovascular and coronary disease and stroke"
author: "Andrew Saul"
date: "5/21/2021"
output:
  bookdown::gitbook:
    lib_dir: assets
    split_by: section
    config:
      toolbar:
        position: static
editor_options: 
  chunk_output_type: console
---
# Background

```{r setup}
knitr::opts_chunk$set(echo = TRUE)
renv::init()
renv::snapshot() # asks if package versions should be saved in lockfile.  If star it means version not recognised.
renv::restore() # restores package versions that were saved using snapshot
# renv::install() #installs packages from cache in preference to cran
.libPaths() #displays paths of librarys on system
find.package() #finds files containing specified package 


```



```{r library, echo=TRUE, warning=FALSE}
suppressPackageStartupMessages(library("tidyverse"))
suppressPackageStartupMessages(library("zoo"))

if(!require("tidyverse")) install.packages("tidyverse")
if(!require("zoo")) install.packages("zoo")

library(tidyverse)
library(readxl)
library(vroom)
library(fs)
library(zoo)                        # used to fill NA values with locf


```



This project was initiated by the author in order to demonstrate data wrangling and exploratory data analysis

### Method
Data of cardiovascular related deaths in the UK were obtained in the form of an excel spreadsheet downloaded from the source "<https://www.ons.gov.uk/peoplepopulationandcommunity/healthandsocialcare/causesofdeath/adhocs> /005268cardiovasculardiseasecoronaryheartdiseaseandstrokedeathsbylocalauthoritydeathsregistered2012to2014".

The population statistics for each locality in England and Wales were also obtained in the form of an excel spreadsheet from the source "<https://data.london.gov.uk/download/ons-mid-year-population-estimates-custom-age-tables/11cff330-73d7-41ef-87c1-9b48337f98f4/ons-mye-custom-age-tool-uk-geogs-2015.xls>".

In order to link the data between these two spreadsheets, only data from England and Wales were wrangled 

### Stage 1

The two excel files were wrangled, cleaned and merged. The code for these procedures is contained in this file "01-data-preparation-ccs.Rmd" and "my_functions\\my_funcs.R".

### Stage 2

The explanatory data analysis code (EDA) is contained in the file "02-EDA.Rmd" utilising the datasets in the file "data\\ccs.RData".  The purpose of this section was demonstrate the possibilites of data visualisation using various ggplot2 packages

### Data wrangling, cleaning, merging and saving

```{r ccs, echo=TRUE, message=FALSE, results="hide", warning=FALSE}
source("my_functions/my_funcs.R")
##Data source directory##

##excel path filename (dirname/filename.ext)##
path_file <- "data/ccs.xls"
subdirectory <- "csv"

#### converts all sheets in xls files to csv files and writes them to directory '<dirname>/<subdirectory>'
# if subdirectory not specified, files saved in same dir as .xls file
xls_to_csvs(path_file, subdirectory) 

#find all files saved to directory <csvspath>
csvspath <- "data/csv"

raw_filelist <- fs::dir_ls(csvspath) #outputs all filenames in directory

## create object containing paths of .csv files
ccs_filenames <- c("data\\ccs_2012.csv", "data\\ccs_2013.csv", "data\\ccs_2014.csv")

## drop csv files that don't conform to format
mod_filelist <- drop_csvs(raw_filelist, "data/csv/ccs_T&C's.csv")
#######################
## work in progress ###
######################
#combine CSV files together, clean data and remove rows containing NA values
df_ccs <- mod_filelist |> 
  map_dfr(csv_add_year)  |>    
  map_dfr(na.locf)  |>      # replaces NA values with cell above - required due to format of xls file
  df_tidy()
```

The object df_ccs is a dataframe of all the localities in the UK.  The population data available only contains localities in England.  For this reason, only localities in England were investigated. 

The age grouping in the ccs deaths dataframe is slightly different than for the population dataframe. As such, age grouping "<1" and "01-04" levels were collapsed together into a new level "0-4".  

```{r pop,  message=FALSE, results="hide", warning=FALSE}
# Only include English localities as we have population data for this
df_ccs_eng <- df_ccs %>%
  dplyr::filter(str_detect(la_new_code, "^E."))

#collapse ages 0-4 to combine with population tibble
df_ccs_eng_collapse <- 
  df_ccs_eng %>%  
  mutate(age = fct_recode(age, "5-9" = "05-09")) %>% 
  mutate(age = fct_collapse(age, "0-4" = c("<1", "01-04"))) %>% 
  group_by(la_new_code, local_authority, year, sex, cause_of_death, age) %>% 
  summarise(freq = sum(freq)) 
```

A check of the levels for each explanatory variable indicated that there are 348 local authorities, 3 years, 2 genders, 3 causes of deaths and 19 age categories.  As such, for each local authority there should be 342 (3*2*3*19) rows of data. Results indicate this is correct for all but the "City of London" local authority which contained only 285 entries (No data for male stroke fatalities in the 3 years of investigation).  As such "City of London" local authority was dropped from the analysis
```{r}
# check factor levels for all fields
df_ccs_eng_collapse %>% 
  str()

#check all regions contain 342 entries (year*sex*cause_of_death*age)
df_ccs_eng_collapse %>% 
  group_by(local_authority) %>% 
  summarise(n=n()) %>% 
  filter(n != 342)

  df_ccs_eng_collapse %>% 
    filter(local_authority == "City of London") %>% 
    View()  #City of London only contained 285 out of the 342 entries.
  # Therefore this LA was dropped from the analysis
  
df_ccs_eng_collapse <- 
  df_ccs_eng_collapse %>% 
    filter(local_authority != "City of London")  
```

Population data was extracted from the excel spreadsheet.

```{r}
#define pathname for population xls file
path_file_pop <- "data\\pop_stand_2012-14.xls"

##write csv files to data\\ directory## 
extract_all_csvs(path_file_pop)


## create object containing paths of population .csv files
popfilename <- c("data\\pop_stand_2012-14_Females.csv", "data\\pop_stand_2012-14_Males.csv")


#tibble containing extracted data from the population excel file
# char fields converted into factors
df_pop <- map_dfr(popfilename, csvpopfile) %>%
  select(-c("area")) %>% 
  mutate(year = as.integer(year), pop = pop) %>% #*1000 represents per person 
  tidy_field_type() %>% 
  rename(la_new_code = code, age = age_group) 
  


################################ To Do ##################################################

#change CODE  to their original values as specified in the notes of the spreadsheet using "recode" command

df_pop <- df_pop %>% mutate(la_new_code = recode(la_new_code, "E06000048" = "E06000057")) %>% 
          mutate(la_new_code = recode(la_new_code, "E08000020" = "E08000037")) %>%  
          mutate(la_new_code = recode(la_new_code, "E07000097" = "E07000242")) %>% 
          mutate(la_new_code = recode(la_new_code, "E07000101" = "E07000243")) %>%
          mutate(la_new_code = recode(la_new_code, "E11000004" = "E11000007"))

# ensure populations have > 0 values
df_pop <- df_pop %>% 
  filter(pop >0)


#fields Local.Authority and AREA joined to become Local.Authority
df_deaths_pop <- left_join(df_ccs_eng_collapse, df_pop, by = c( "la_new_code", "age", "year", "sex" )) %>% 
  mutate(age = factor(age, ordered = TRUE))


#check no. NA values in tibble
#na.omit(df_deaths_pop) 
#same number of values in tibble therefore no NA values present in df_deaths_pop

save(df_ccs, df_ccs_eng, df_ccs_eng_collapse, df_pop, df_deaths_pop, file = "data\\ccs.RData" )
```

Tibbles of possible interest are saved in file "data\\ccs.RData". These are utilised in the Explanatory Data Analysis section
