---
title: "Exploratory Data Analysis"
author: "AS"
date: "5/21/2021"
output:
  bookdown::pdf_book:
    toc: false
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning=FALSE)
```
# Introduction

```{r libraries, include=FALSE}
options(tidyverse.quiet = TRUE,  warn.conflicts = FALSE)

library(tidyverse)
library(broom)
library(scales)  #wrap_format
if(!require("patchwork")) install.packages("patchwork")
library(patchwork)
#library(rlang)
load("data\\ccs.RData")
source("my_functions\\my_funcs.R")
```


Before visualising the data a check was performed to ensure all local_authority population entries in the combined population/death tibble (df_deaths_pop) contained a  value greater than 0.  There were 129 entries that contained NA values, all of which were registered for the Isle of Scilly. For each local_authority there should be 19 (age) $\times$ 3 (cause of death) $\times$ 2 (sex) $\times$ 3 (year) entries, totalling 342.  As 38% of Isle of Scilly entries were not complete, this locality was removed from analysis of EDA Rates \@ref(rates).

```{r}
# df_deaths_pop %>% 
#   filter(pop <= 0) %>%
#   View()
# 
# df_deaths_pop %>% 
#   filter(is.na(pop)) %>%
#   View()
```

# EDA deaths
The individual variables year, age, cause of death, locality and sex of deaths were explored using visualisations.  In addition, combination of variables were also investigated.  In order to achieve this summary measures for each variable and variable combinations were obtained and stored in R objects (see 02-EDA.Rmd file for code).

```{r summaries, include=FALSE}
############## Summaries #########################################################################
summ_age_year_eng <-  sum_func(age, year=as_factor(year))
summ_age_sex_year_eng <- sum_func(age, sex, year=as_factor(year))
summ_sex_year_eng <- sum_func(sex, year=as_factor(year))
summ_cod_year_eng <- sum_func(cause_of_death, year=as_factor(year)) |> 
  mutate(freq = freq/1000)
summ_cod_sex_year_eng <- sum_func(cause_of_death, sex, year=as_factor(year))|> 
  mutate(freq = freq/1000)
summ_loc_eng <-  sum_func(local_authority) %>% 
  arrange(freq = desc(freq))

summ_age_year_type <- sum_func(age, cause_of_death, year = as_factor(year))
summ_age_year_sex_type <- sum_func(age, cause_of_death, sex, year = as_factor(year))
summ_year_eng <-  sum_func(year = as_factor(year)) 
```

As there were 347 localities investigated in this dataset, only 10 with the most frequency of deaths for both males and females were displayed in a plot. An R object was created to store this data (see 02-EDA.Rmd file).  Table \@ref(tab:largest-deaths-loc) displays this data.

```{r largest-deaths-loc}
##################################                           #####################################

# filter localities differentiated by sex with deaths from hi to low 
loc_sex <- sum_func(local_authority, sex) %>% 
  arrange(freq = desc(freq))

#top 10 localities with highest deaths either by male or female
#names of top 10 localities without discriminating by sex 
names_loc <- summ_loc_eng |> 
  head(10) |> 
   pull(local_authority) 

#names of top 10 localities either by male or female
names_loc_sex <- loc_sex %>%
  head(18) %>% 
  pull(local_authority) %>% 
  unique()

#no difference between the 2 sorting methods
setdiff(names_loc, names_loc_sex)
  
loc_sex_top10 <- loc_sex %>% 
  filter(local_authority %in% names_loc_sex)

loc_sex_top10 |> 
  knitr::kable(caption = "The top ten Local Authorities with largest overall deaths due to cardiovascular disease, coronary artery disease or stroke, stratified by sex.")


```


Overall Birmingham contained the largest frequency of deaths for both males and females.  For later analysis of death rates, Birmingham was used as the reference region that other local_authorities were compared against.


```{r}


####################################################################################
####### breakdown of birmingham#####################################
birm <- df_deaths_pop %>% 
  filter(local_authority == "Birmingham") %>% 
   sum_func(age, sex, cause_of_death,  year=as_factor(year), data =.)

```

Individual plots were constructed (see 02-EDA.Rmd for code) and saved in R objects.  They are later used in this report using the R package "patchwork".

```{r plots, include=FALSE}
######################################################################################################
##################### Plots ##########################################################################

# bar plots
#dodge displays distribution of css deaths per age group for the three years
p_age <- summ_age_year_eng %>%   
  ggplot(aes(x=age, y=freq, fill = year))+  
  geom_bar(stat="identity", position = position_dodge())+
  labs(y = "Frequency")+
  scale_x_discrete(labels = wrap_format(10))+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 90), legend.position = "top")

p_age_sex <- summ_age_sex_year_eng %>%   
  ggplot(aes(x=age, y=freq, fill = year))+  
  geom_bar(stat="identity", position = position_dodge(), show.legend = FALSE)+
  labs(x= "age group", y = "Frequency")+
  scale_x_discrete(labels = wrap_format(10),
  breaks = c("0-4", "10-14", "20-24", "30-34", "40-44", "50-54", "60-64", "70-74", "80-84", "90+"))+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 90))+
  facet_wrap(vars(sex))


p_type <- summ_cod_year_eng %>%   
  ggplot(aes(x=cause_of_death, y=freq, fill = year))+  
  geom_bar(stat="identity", position = position_dodge())+
  labs(y= "Frequency ('000)", x = "")+
  scale_x_discrete(labels = wrap_format(10))+
  theme_bw()+
  theme(legend.position = "top", axis.text = element_text(size = 18),
        axis.title = element_text(size = 20))

p_type_sex <- summ_cod_sex_year_eng %>%   
  ggplot(aes(x=cause_of_death, y=freq, fill = year))+  
  geom_bar(stat="identity", position = position_dodge(), show.legend = FALSE)+
  labs(y= "Frequency ('000)", x = "Disease type")+
  scale_x_discrete(labels = wrap_format(10))+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 90, size = 14), axis.text.y = element_text(size=18),
        axis.title = element_text(size = 20))+
  facet_wrap(vars(sex))

p_loc <- summ_loc_eng %>% 
  ggplot(aes(y=fct_reorder(local_authority, freq), x=freq))+  
  geom_bar(stat="identity")+
  labs(y= "", x = "Deaths")+
  theme_bw()+
  theme(axis.text.y = element_blank())

p_loc_10 <- summ_loc_eng %>% 
  head(10) %>% 
  ggplot(aes(x=freq, fct_reorder(local_authority, freq)))+  
  geom_bar(stat="identity")+
  labs(y= "", x = "Deaths")+
  #scale_y_discrete(limits = rev)+
   # coord_flip()
  theme_bw()+
  theme(axis.text.x = element_text(angle = 0))
  
p_loc_sex_top10 <-  loc_sex_top10 %>% 
   ggplot(aes(x=freq, fct_reorder(local_authority, freq)))+
   geom_bar(stat="identity")+
  labs(y= "", x = "Deaths")+
  #coord_flip()+
   #scale_y_discrete(limits = rev)+
  theme(axis.text.x = element_text(angle = 0))+
  theme_bw()+
   facet_wrap(vars(sex))


```

# Plots
 
```{r age, fig.height = 8, fig.cap="The effect of age and sex on frequency of death ", echo=FALSE}
p_all <- ((p_age / p_age_sex))
p_all + plot_annotation(
  tag_levels = "A"
)
```

Figure \@ref(fig:age) A demonstrated that increased age was associated with increased deaths. This would be expected. Very few deaths occur before the age group 40-44. Also noted in this figure was the small decline in deaths across the older age groups from years 2012 to 2014. When stratifying by sex (figure \@ref(fig:age) B) it was interesting to note that the peak age group of male deaths was 80-84, after which there was a decline.  This may be due to a reduced male population at these age groups, and therefore less males would have been likely to die. 


```{r type, fig.width = 10, fig.height = 10, fig.cap="The effect of disease type and sex on frequency of deaths in England", echo=FALSE}
p_type_all <- ((p_type / p_type_sex))
p_type_all + plot_annotation(
    tag_levels = "A"
  )
```

Figure \@ref(fig:type) A demonstrated around twice the number of deaths due to cardiovascular disease than coronary heart disease, and there were fewer stroke deaths than coronary heart disease deaths.  The number of cardiovascular disease deaths in England in 2012 was slightly under 132,000.  There was a slight decrease in deaths for all groups from 2012 to 2014.  Figure \@ref(fig:type) B demonstrated an interesting feature.  Males were likely to suffer from greater coronary heart disease deaths than females.  However, females were more likely to die of stroke than males.  


```{r local, fig.height = 8, fig.cap="Local authorities with the top 10 frequencies of deaths in England"}
p_loc_all <- p_loc_10/p_loc_sex_top10
p_loc_all +
  plot_annotation(
    tag_levels = "A"
  )
```

Figure \@ref(fig:local) A demonstrated the top 10 localities where deaths are highest in England.  Birmingham experienced the highest number of deaths by a considerable margin compared to the locality with the next highest frequency of deaths, Leeds.  Apart from Cornwall (3rd) and Wiltshire (7th), all the remaining eight localities were located in the Midlands and north of England.  Stratifying these figures according to sex (figure \@ref(fig:local) B), more females died of the three types of diseases in Cornwall, Wiltshire and East Riding of Yorkshire. In the seven other regions more males died than females.  

```{r birm, fig.height = 8, fig.cap="Deaths in Birmingham for each sex caused by the three types of diseases"}
birm %>% 
   ggplot(aes(y=freq, x =age))+
   geom_bar(stat="identity")+
  labs(x= "age group", y = "Frequency",
       title = "Birmingham")+
  #coord_flip()+
   scale_y_continuous(limits = c(0,1000))+
  scale_x_discrete(breaks = c("0-4", "10-14", "20-24", "30-34", "40-44", "50-54", "60-64", "70-74", "80-84", "90+"))+
  theme_bw()+
  theme(strip.background = element_rect(fill = "white"),
    axis.text.x = element_text(angle = 90))+
 # theme_bw()+
   facet_grid(sex~cause_of_death, scales = "fixed")
```

According to figure \@ref(fig:birm)  there were greater female deaths Birmingham due to cardiovascular disease in the 85-89 and 90+ age group. Otherwise males deaths were greater for age groups between 40-44 and 80-84.  Lower number of male deaths for coronary artery disease were recorded in the 90+ age group, while for age groups between 40-44 and 85-90 it appeared more male deaths occured compared to femailes. Likewise, there appears an increase in coronary heart disease in females in the 90+ age group.  Interestingly, more females are likely to die of stroke compared to males for age groups 75-79 and above.

One reason for the earlier age_group deaths of males in the industrial cities could be due to the historic work environments. 



```{r loc-year-changes, fig.height=8, fig.cap="Changes in frequency of deaths in localities with highest amounts of deaths"}
#summary of deaths by locality and year
top10_loc <- df_ccs_eng_collapse |> 
  filter(local_authority %in% names_loc) |> 
  group_by(local_authority, year) |> 
  summarise(freq = sum(freq))  |> 
  mutate(local_authority = fct_recode(local_authority,"East Riding of York." = "East Riding of Yorkshire"))

top10_year_p <- top10_loc |> 
  ggplot(aes(x=year, y = freq, colour = local_authority))+
  geom_line()+
  scale_x_continuous(breaks = c(2012,2013,2014))+
  scale_y_continuous(breaks = seq(1500, 4500, 1000))+
  labs(y="Frequency")+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5))+
  facet_wrap(vars(local_authority), nrow = 5)
  
  top10_year_p

```

Figure \@ref(fig:loc-year-changes) indicates changes in deaths per year for the local_authorities with the highest frequencies of deaths. Frequencies in Birmingham, Leeds , Cheshire East and Sheffield appear to have decreased year on year.  In Durham, Cornwall and Bradford, deaths appeared to increase in 2013 but then decreased in 2014. For East Riding of Yorkshire, Kirkless and Wiltshire, death frequencies appeared stable over the three years. 
```{r agetypeyear, fig.height = 8, fig.cap="Deaths due to the three types of diseases investigated in England for age groups 30-34 and greater" }
# remove age groups with low frequencies
select_age <- summ_age_year_eng %>% 
  select(age) %>% 
  unique() %>% 
  tail(13) %>% 
  pull()

p_age_type <- summ_age_year_type %>% 
  filter(age %in% select_age) %>% 
  mutate(freq = freq/1000) |> 
  ggplot(aes(x=age, y=freq, fill = year))+  
  geom_bar(stat="identity", position = position_dodge(), show.legend = FALSE)+
  labs(x= "age group", y = "Frequency ('000)")+
  theme_bw()+
  theme(strip.background = element_rect(
     color="black", fill="white", size=1, linetype="solid"),
    axis.text.x = element_text(angle = 90), legend.position = "top")+
  facet_wrap(vars(cause_of_death), nrow = 3)

p_age_type
```

Looking at the relationship between age group and type of death (figure \@ref(fig:agetypeyear)), it was seen that deaths increased in an exponential manner for age groups in  both cardiovascular disease and stroke.  However, it was noticeable that there was a slight decrease in deaths for coronary heart disease in the age group 90+.  When stratifying for sex, it was seen in figure \@ref(fig:agetypesexyear) that deaths due to cardiovascular disease  and stroke was much greater in females than males at older age group.  This would likely be due to the longer life-span of females. More males than females died of coronary heart disease at age groups younger than 90+, possibly due to poorer lifestyle.  At the age_group 90+ many more women died than men, likely due to more women living at this age.

```{r agetypesexyear, fig.height = 8, fig.cap="Deaths due to disease type between sexes in England"}
p_age_sex_type <- summ_age_year_sex_type %>% 
  filter(age %in% select_age) %>%
  mutate(freq = freq/1000, cause_of_death = fct_recode(cause_of_death,
                                                       "cardiovascular" = "cardiovascular disease",
                                                       "coronary" = "coronary heart disease",
                                                       "stroke" = "stroke") ) |> 
  
  ggplot(aes(x=age, y=freq, fill = year))+  
  geom_bar(stat="identity", position = position_dodge())+
  labs(x= "age group", y = "Frequency ('000)")+
  scale_x_discrete(breaks = c("0-4", "10-14", "20-24", "30-34", "40-44", "50-54", "60-64", "70-74", "80-84", "90+"))+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 90))+
  facet_grid((cause_of_death)~(sex), scales = "free_y")

p_age_sex_type
```

<!-- ## EDA of Rates {#rates} -->


<!-- ```{r} -->
<!-- #A check of population data where entries are NA or 0. -->
<!-- df_deaths_pop %>%  -->
<!--   #filter(local_authority == "Isles of Scilly") %>%  -->
<!--   filter(is.na(pop)|0) %>%  -->
<!--   select(local_authority) %>% -->
<!--   group_by(local_authority) %>%  -->
<!--   tally() -->

<!-- df_deaths_pop %>%  -->
<!--   filter(pop == is.na(pop)|0) %>%  -->
<!--   select(cause_of_death) %>% #interchange age with local authority, sex and cause of death to check for 0 entries -->
<!--   distinct() -->
<!-- ``` -->

<!-- ### Crude rates  -->
<!-- For reasons explained previously, the localities of  "City of London" and "Isles of Scilly" have  not been included in the Rates analysis. -->

<!-- ```{r} -->
<!-- #create rate variable - remove Isle of Scilly data -->
<!-- df_deaths_rate <- df_deaths_pop %>%  -->
<!--   filter(local_authority != "Isles of Scilly")  -->

<!-- ``` -->

<!-- The crude deaths rates of Isle of Scilly and City of London for ages below  75 are substantially higher than for the next highest locality, Rutland.  Six entries are present in data for "Isle of Scilly", and seventeen entries are present for "City of London".  The mean population for  -->

<!-- ```{r} -->
<!-- ########################Crude rates################################### -->

<!-- #local authority (age/sex) -->
<!-- la_cr <- df_deaths_rate %>%  -->
<!--   group_by(local_authority) %>%  -->
<!--   summarise(All_ages_cruderate = sum(freq)/sum(pop)) %>%  -->
<!--   arrange(desc(All_ages_cruderate)) -->

<!-- cod_cr <- df_deaths_rate %>%  -->
<!--   group_by(cause_of_death) %>%  -->
<!--   summarise(All_ages_cruderate = sum(freq)/sum(pop)) %>%  -->
<!--   arrange(desc(All_ages_cruderate)) -->

<!-- ######################################################################## -->
<!-- ###### Directly Standardised Rate (DSR)################################ -->
<!-- ## requires standard population --- Birmingham pop used as standard ##### -->
<!-- ######################################################################### -->
<!-- stand_pop <- df_deaths_pop %>%  -->
<!--   filter(local_authority == "Birmingham") %>% -->
<!--   group_by(age, sex, year) %>%  -->
<!--   summarise(standard.pop = pop, standard.freq = sum(freq)) %>%  -->
<!--   distinct()  -->



<!-- df_deaths_cif <- df_deaths_rate %>% -->
<!--   group_by(age, sex, year, local_authority) %>%  -->
<!--   summarise(freq = sum(freq), pop = pop) %>%  -->
<!--   distinct() %>%  -->
<!--   left_join(stand_pop, by = c("age", "sex", "year")) -->

<!-- #comparative incidence figure -->
<!-- CIF_la <- df_deaths_cif %>%  -->
<!--   #filter(local_authority == "Birmingham") %>%  -->
<!--   mutate(Expected_cases = freq/pop*standard.pop) %>%  -->
<!--   group_by(local_authority, year) %>%  -->
<!--   summarise(CIF = sum(Expected_cases)/sum(standard.freq)) -->

<!-- ### view all CIF localities (age/sex) and plot per time########## -->
<!-- CIF_la %>%  -->
<!--   arrange(desc(CIF)) %>%  -->
<!--   View() -->


<!-- ################################################################### -->
<!-- ##### standard pop for cod is cardiovascular disease ################ -->
<!-- cod.stand.pop <-  -->
<!--   df_deaths_rate %>%  -->
<!--   filter(cause_of_death == "cardiovascular disease") %>%  -->
<!--  # ungroup %>%  -->
<!--   group_by(age, sex, year) %>%  -->
<!--   summarise(cod.stand.pop = sum(pop), cod.stand.freq = sum(freq))  -->

<!-- df_death_cod.rates <- df_deaths_rate %>% -->
<!-- #  ungroup %>%  -->
<!--   group_by(year, sex, cause_of_death, age) %>%  -->
<!--   summarize(freq = sum(freq), pop = sum(pop)) %>%  -->
<!--   left_join(cod.stand.pop, by = c("age", "sex", "year")) -->

<!-- CIF_cod <- df_death_cod.rates %>%  -->
<!--   mutate(Expected_cases = freq/pop*cod.stand.pop) %>%  -->
<!--   group_by(cause_of_death, year) %>%  -->
<!--   summarise(CIF = sum(Expected_cases)/sum(cod.stand.freq)) -->


<!-- ``` -->

<!-- ```{r} -->

<!-- ``` -->


<!-- ```{r} -->
<!-- rate_age_year_eng <-  rate_func(age, year=as_factor(year)) -->
<!-- rate_age_sex_year_eng <- rate_func(age, sex, year=as_factor(year)) -->
<!-- rate_sex_year_eng <- rate_func(sex, year=as_factor(year)) -->
<!-- rate_cod_year_eng <- rate_func(cause_of_death, year=as_factor(year)) -->
<!-- rate_cod_sex_year_eng <- rate_func(cause_of_death, sex, year=as_factor(year)) -->
<!-- rate_loc_eng <-  rate_func(local_authority) %>%  -->
<!--   arrange(death_rate = desc(death_rate)) -->

<!-- rate_age_year_type <- rate_func(age, cause_of_death, year = as_factor(year)) -->
<!-- rate_age_year_sex_type <- rate_func(age, cause_of_death, sex, year = as_factor(year)) -->
<!-- rate_year_eng <-  rate_func(year = as_factor(year))  -->

<!-- ##################################                           ##################################### -->

<!-- # filter localities differentiated by sex with deaths from hi to low  -->
<!-- rate_loc_sex <- rate_func(local_authority, sex) %>%  -->
<!--   arrange(death_rate = desc(death_rate)) -->

<!-- #top 10 localities with highest deaths either by male or female -->
<!-- rate_names_loc_sex <- rate_loc_sex %>%  -->
<!--   head(18) %>%  -->
<!--   pull(local_authority) %>%  -->
<!--   unique() -->

<!-- rate_loc_sex_top10 <- rate_loc_sex %>%  -->
<!--   filter(local_authority %in% rate_names_loc_sex) -->

<!-- #################################################################################### -->
<!-- ####### breakdown of birmingham and Cornwell -->
<!-- # birm <- df_deaths_pop %>%  -->
<!-- #   filter(local_authority == "Birmingham") %>%  -->
<!-- #    rate_func(age, sex, cause_of_death,  year=as_factor(year), data =.) -->
<!-- #  -->
<!-- # corn <- df_deaths_pop %>%  -->
<!-- #   filter(local_authority == "Cornwall") %>%  -->
<!-- #    rate_func(age, sex, cause_of_death, year=as_factor(year), data = .) -->


<!-- ``` -->

<!-- ```{r} -->
<!-- ###################################################################################################### -->
<!-- ##################### Plots ########################################################################## -->

<!-- # bar plots -->
<!-- #dodge displays distribution of css deaths per age group for the three years -->
<!-- r_age <- rate_age_year_eng %>%    -->
<!--   ggplot(aes(x=age, y=death_rate, fill = year))+   -->
<!--   geom_bar(stat="identity", position = position_dodge())+ -->
<!--   labs(x= "age group", y = "Death rates (per 1,000)")+ -->
<!--   theme_bw()+ -->
<!--   theme(axis.text.x = element_text(angle = 90)) -->

<!-- r_age_sex <- rate_age_sex_year_eng %>%    -->
<!--   ggplot(aes(x=age, y=death_rate, fill = year))+   -->
<!--   geom_bar(stat="identity", position = position_dodge())+ -->
<!--   labs(x= "age group", y = "Death rates (per 1,000)")+ -->
<!--   theme_bw()+ -->
<!--   theme(axis.text.x = element_text(angle = 90))+ -->
<!--   facet_wrap(vars(sex)) -->


<!-- r_type <- rate_cod_year_eng %>%    -->
<!--   ggplot(aes(x=cause_of_death, y=death_rate, fill = year))+   -->
<!--   geom_bar(stat="identity", position = position_dodge())+ -->
<!--   labs(x= "Cause of death", y = "Death rates (per 1,000)")+ -->
<!--   scale_x_discrete(labels = wrap_format(10))+ -->
<!--   theme_bw() -->



<!-- r_type_sex <- rate_cod_sex_year_eng %>%    -->
<!--   ggplot(aes(x=cause_of_death, y=death_rate, fill = year))+   -->
<!--   geom_bar(stat="identity", position = position_dodge())+ -->
<!--   labs(y = "Death rates (per 1,000)", x = "type of death")+ -->
<!--   scale_x_discrete(labels = wrap_format(10))+ -->
<!--   theme_bw()+ -->
<!--   theme(axis.text.x = element_text(angle = 90))+ -->
<!--   facet_wrap(vars(sex)) -->

<!-- r_loc <- rate_loc_eng %>%  -->
<!--   ggplot(aes(y=fct_reorder(local_authority, death_rate), x=death_rate))+   -->
<!--   geom_bar(stat="identity")+ -->
<!--   labs(y = "Death rates (per 1,000)", x = "Deaths")+ -->
<!--   theme_bw()+ -->
<!--   theme(axis.text.y = element_blank()) -->

<!-- r_loc_10 <- rate_loc_eng %>%  -->
<!--   head(10) %>%  -->
<!--   ggplot(aes(x=death_rate, fct_reorder(local_authority, death_rate)))+   -->
<!--   geom_bar(stat="identity")+ -->
<!--   labs(y= "", x = "Death rates (per 1,000)")+ -->
<!--   #scale_y_discrete(limits = rev)+ -->
<!--    # coord_flip() -->
<!--   theme_bw()+ -->
<!--   theme(axis.text.x = element_text(angle = 0)) -->

<!-- r_loc_sex_top10 <-  rate_loc_sex_top10 %>%  -->
<!--    ggplot(aes(x=death_rate, fct_reorder(local_authority, death_rate)))+ -->
<!--    geom_bar(stat="identity")+ -->
<!--   labs(y= "", x = "Death rates (per 1,000)")+ -->
<!--   #coord_flip()+ -->
<!--    #scale_y_discrete(limits = rev)+ -->
<!--   theme(axis.text.x = element_text(angle = 0))+ -->
<!--   theme_bw()+ -->
<!--    facet_wrap(vars(sex)) -->

<!-- df_deaths_pop %>%  -->
<!--   filter(local_authority == "Isles of Scilly") %>%  -->
<!--   summarise(pop = sum(pop)) -->
<!-- #total pop in I of S is 60,000 -->

<!-- ``` -->
